Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
getting rid of extraneous adverbs
z is height

Group fluxes are shown in \Cref{fig:group1,fig:group2}. The effect of the vacuum
boundary conditions is shown clearly in the cosinusoidal shapes in radial and
axial directions. Both the fast and thermal fluxes are striated, with
the fast group preferring the fuel and the thermal group preferring the moderator.

@@

The effect of the advecting fuel is seen in \Cref{fig:temp} where the temperature
rises steadily with increasing z-coordinate. As is expected, the temperature
gradient is negative in the radial direction.

>>>>

Group fluxes are shown in \Cref{fig:group1,fig:group2}. The effect of the vacuum
boundary conditions is shown by the cosinusoidal shapes in radial and
axial directions. Both the fast and thermal fluxes are striated, with
the fast group preferring the fuel and the thermal group preferring the moderator.

@@

The effect of the advecting fuel is seen in \Cref{fig:temp} where the temperature
rises along the reactor height. As is expected, the temperature
gradient is negative in the radial direction.
